Type Refinements for the Working Class

### 2016-01-01 paper.tex
wordsmithing

Mark Bickford introduced in~\cite{bickford:2008} a type in Nuprl that expresses
the independence of a term $M$ of type $A$ from a symbol $a$, written
$M:A\parallel a$, which is used in order to express the notion that some agent
is not aware of a particular token/atom. In our setting, nominal independence
is best expressed through a comonadic refinement modality, $\Indep{\phi}{a}$, whose
inhabitants are the inhabitants of $\phi$ which do not make use of the symbol
$a$. To be precise, we intend to explain the following refinement formation
rule:
\[
  \infer={
    \Refines{\Upsilon,a:\sigma}{\Indep{\phi}{a}}{\tau}
  }{
    \Refines{\Upsilon,a:\sigma}{\phi}{\tau}
  }
\]

>>>>

Mark Bickford introduced in~\cite{bickford:2008} a type in Nuprl that expresses
the independence of a term $M$ of type $A$ from a symbol $a$, written
$M:A\parallel a$, which is used in order to express the notion that some agent
is not aware of a particular token/atom. In our setting, nominal independence
is best expressed through a comonadic refinement modality, $\Indep{\phi}{a}$, whose
inhabitants are those of $\phi$ which do not make use of the symbol
$a$. To be precise, we intend to explain the following refinement formation
rule:
\[
  \infer={
    \Refines{\Upsilon,a:\sigma}{\Indep{\phi}{a}}{\tau}
  }{
    \Refines{\Upsilon,a:\sigma}{\phi}{\tau}
  }
\]
